Understanding Factors That Affects the Existence of Digital Innovation Hubs

### 2024-12-01 paper/paper.qmd
Modified Abstract

---
title: "Understanding Factors That Affects the Existence of Digital Innovation Hubs"
subtitle: "An Analysis of Toronto Libraries' Data"
author: "Yanzun Jiang"
thanks: "Code and data are available at: [https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries](https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Understanding Factors That Affects the Existence of Digital Innovation Hubs"
subtitle: "An Analysis of Toronto Libraries' Data"
author: "Yanzun Jiang"
thanks: "Code and data are available at: [https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries](https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries)."
date: today
date-format: long
abstract: "This paper investigates what influences the presence of Digital Innovation Hubs (DIHs) in libraries, focusing on factors such as parking availability, workstations, library size, and age. Using a logistic regression model, we found that libraries with more parking and workstations are more likely to have DIHs, while older libraries are less likely to include them. These findings highlight the importance of modern facilities and adequate resources in fostering digital innovation within libraries. This research can guide library planners and policymakers in improving library services and ensuring access to technological opportunities for communities."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
